Learning constraints in tabular data

### 2016-05-11 Paper/ECAI/tabular.tex
style correction

{\it
\textbf{Motivation}:
\begin{itemize}
  \item USED -- File generated from model, model got lost, need to reconstruct
  \item Constraint programming is hard - is Excel hard?
  \item Avoid manual analysis, provide selection of constraints
  \item SOMEWHAT USED --Error checking
  \item Completion, gain speed and insights (Complicated constraints, also complicated to verify, too much output)
\end{itemize}

\textbf{Novelty:}
\begin{itemize}
  \item USED -- Unsupervised setting (contrary to flashfill, etc)
  \item Numeric, different constraints (contrary to single textual function solution in flashfill, etc)
  \item USED -- Data format (2D) -- data is no longer in rows like a classic ML or DM settings
  \item USED -- Declarative, general / modular, stacking of constraint problems
\end{itemize}

\begin{figure*}[tbh]
  \begin{center}
    \includegraphics[width=0.75\textwidth]{figures/Demo.png}
  \end{center}
  \vspace{-10pt}
  \caption{Example spreadsheet (black words and numbers only). Blue and green elements are added by us to clarify the relations.}
  \label{fig:main_example}
\end{figure*}
}

@@

%\bibliographystyle{ecai}
\bibliography{references}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% {\it
% \textbf{Motivation}:
% \begin{itemize}
%   \item USED -- File generated from model, model got lost, need to reconstruct
%   \item Constraint programming is hard - is Excel hard?
%   \item Avoid manual analysis, provide selection of constraints
%   \item SOMEWHAT USED --Error checking
%   \item Completion, gain speed and insights (Complicated constraints, also complicated to verify, too much output)
% \end{itemize}

% \textbf{Novelty:}
% \begin{itemize}
%   \item USED -- Unsupervised setting (contrary to flashfill, etc)
%   \item Numeric, different constraints (contrary to single textual function solution in flashfill, etc)
%   \item USED -- Data format (2D) -- data is no longer in rows like a classic ML or DM settings
%   \item USED -- Declarative, general / modular, stacking of constraint problems
% \end{itemize}
%}

\begin{figure*}[tbh]
  \begin{center}
    \includegraphics[width=0.75\textwidth]{figures/Demo.png}
  \end{center}
  \vspace{-10pt}
  \caption{Example spreadsheet (black words and numbers only). Blue and green elements are added by us to clarify the relations.}
  \label{fig:main_example}
\end{figure*}

@@

\bibliographystyle{plain}
\bibliography{references}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
